Blueprint for efficient nuclear spin characterization in color center

### 2024-02-02 article.tex
paper text fininshed draft

%%%%%%%%%%%%%%%%%%%================= %THEORY
\section{Results}
\label{sec:theory}
%%%%%%%%%%%%%%%Í%%%%=================
We consider a central spin system of \textit{non-interacting} nuclear spins $I=1/2$ coupled to the central electron spin $\boldsymbol{S}$.
The central electron spin is manipulated resonantly with microwave pulses, which transfer the population between the two sublevels denoted as $m_s=s_0$ and $m_s = s_1$.
These two spin sublevels are separated due to the Zeeman effect and/or zero-field splitting, forming a two-level subsystem with an energy splitting of $\omega_a$.
The Hamiltonian of the system in the secular approximation and in the rotating frame of the applied microwave $\omega_{mw}$ can be written as:
\begin{align}
	H = \Delta S_z + \sum_k (\omega_L^{(k)}  + A_{zz}^{(k)} S_z) I_z^{(k)} + A_{zx}^{(k)} S_z I_x^{(k)}
	\label{eq:H}
\end{align}
Where $\Delta = \omega_a - \omega_{mw}$ is the detuning, $\omega_L^{(k)} =\gamma_n^{(k)} B$ is the nuclear Rabi frequency with $\gamma_n^{(k)}$ being the nuclear spin gyromagnetic ratio and $B$ the external magnetic field, and $A_{zz}$ and $A_{zx}$ are the parallel and perpendicular secular components of the hyperfine tensor, respectively.
The Hamiltonian is diagonal in the electron spin subspace, thus the Hamiltonian for the nuclear spins could be rewritten in the electron spin subdomains $s_i$ ($i=0,1$).
The nuclear spin Hamiltonian could be solved for eigenenergies, which determine the precession frequencies of $\omega_i = \sqrt{(\omega_L + s_i A_{zz})^2+ (s_i A_{zx})^2}$, $i=0,1$ along the eigenvector axes $\vec{n}i =(\frac{s_i A{zx}}{\omega_i}, 0, \frac{\omega_L + s_i A_{zz}} {\omega_i})$.
It is assumed that the pulse duration $t_p$ is short enough ($\omega_L t_p \ll 1$) that the nuclear spin dynamics during this time is negligible.
For completeness, we start our analysis with the simplest characterization sequence, which is the electron spin Ramsey sequence (free induction decay of the electron) (see the Appendix for derivation).
The Ramsey signal can be obtained as follows:
\begin{gather}
	\expval{\sigma_z}_{Ram} = \cos(\Delta \tau) \prod_{j=1}^{n} \Big[ \cos(\frac{\omega_0 \tau}{2}) \cos(\frac{\omega_1 \tau}{2})+ \notag \\
	(\vec{n_0}\cdot \vec{n_1})\sin(\frac{\omega_0 \tau}{2}) \sin(\frac{\omega_1 \tau}{2}) \Big]^{(j)}
	\textcolor{gray}{e^{-(\frac{\tau}{T_2^\ast})^m}}
\end{gather}	
The exponential decay is introduced to note the Ramsey signal decays with the electron spin $T_2^\ast$ since the formalism does not account for any relaxation processes. The Ramsey sequence is sensitive to detuning since the electron spin is not refocused; however, it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\

@@

Although the Dynamical Decoupling (DD) sequence is well understood and used to characterize nuclear spins, it is not applicable to all systems.
First, DD only works for defects with high magnetic fields and low hyperfine coupling ($\omega_L \gg A_{zz}, A_{zx}$).
Second, the signal is limited to the electron spin $T_2$, which only gradually approaches $T_1$.
Third, signal analysis is rather complicated and time-consuming; one has to collect enough data to ensure that no two nuclear spins overlap in the signal.
Fourth, this sequence does not work for spin 1/2 systems, such as group IV defects in diamond, since the parallel component of the hyperfine coupling cancels their effect on the first order electron spin signal.
Hence, the resonance signal depends on the second order of the perpendicular hyperfine component.

\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} assuming the electron spin is a. spin 1 system b. spin 1/2 system. Simulated Fisher information matrix for the case of the electron spin c. spin 1 system d. spin 1/2 system.}
		\label{fig:3}
	\end{center}
\end{figure*}
In this work, we consider the 23-nuclear spin cluster characterized in paper \cite{abobeih2019atomic} as a realistic case for our comparison.
First, we apply this to the dynamical decoupling sequence and visualize the obtained results. Fig \ref{fig:3} compares the DD signal for the same nuclear spin register but different defects in diamond.
An intuitive description of the sensitivity of a sequence to the variation of hyperfine coupling could be estimated by considering the width and sensitivity of the position of the resonances.
First, we consider the case of an NV center in diamond. The width of a dip is $\delta \tau = \frac{A_{zx}}{\omega_L^2}$. Taking the derivative of the resonance time, we define the sensitivity of the longitudinal hyperfine coupling as follows, using Eq. \ref{eq:resonance} to simplify:
\begin{gather}
	\delta A_{zz} \equiv \frac{\delta \tau}{\abs{\frac{\partial \tau_p}{\partial A_{zz}}}} = \frac{2}{\tau_p} \frac{A_{zx}}{\omega_L} \ge \frac{4}{T_2^{HE}} \frac{A_{zx}}{\omega_L}
\end{gather}
If we assume typical values of $T_2^{HE} = 100$ $\mu$s and $\omega_L=500$ kHz, a weakly coupled nuclear spin $A_{zx}=5$ kHz can be distinguished from another weakly coupled nuclear spin with $\delta A_{zz} = 400$ Hz.
For $S=1/2$, such as group IV defects in diamond, the resonance times are sensitive to the second order of $A_{zx}$ and show no sensitivity to $A_{zz}$.
Hence, even at large $\tau$, the resonances related to nuclear spins will not be well separated.
We define the sensitivity for the spin one-half system as follows:
\begin{gather}
	\delta A_{zx} \equiv \frac{\delta \tau}{\abs{\frac{\partial \tau_k}{\partial A_{zx}}}} = \frac{4}{\tau_k} \ge \frac{8}{T_2^{HE}}
\end{gather}
Assuming typical values of $T_2^{HE} = 100$ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate and approximately 160 times worse than for $S=1$.

To quantify the difference in sensitivity to estimating the hyperfine parameters, we perform calculations of the Fisher Information Matrix (FIM) for the 23-nuclear spin cluster, with 23 $A_{zz}$ and 23 $A_{zx}$ parameters (see Fig. \ref{fig:3}c,d).
The Fisher Information Matrix is estimated for the probability to measure state $|0\rangle$ and reads as: 
\begin{equation}
	F_{ij}(\textbf{A})=\sum_\tau \frac{\partial p(0, \tau, \textbf{A})}{\partial A_i}\frac{\partial p(0, \tau, \textbf{A})}{ \partial A_j} \frac{1}{p (1-p)}.
\end{equation}
For the typical case of an NV center with $S=1$, since all the nuclear spin resonances are clearly resolved, the Fisher Information Matrix takes a diagonal shape, revealing low covariance between the various nuclear spin resonances.
There is crosstalk between $A_{zz}$ and $A_{zx}$ for a nuclear spin, as the position of the peaks depends on both values.
The Fisher Information provides a bound for the precision of parameter estimation, known as the Cramér–Rao bound: 
\begin{equation}
	\delta A^2 \ge \frac{1}{F(A) N}
\end{equation}
For the presented protocol, the precision for various spins is limited by 0.09 Hz \vvv{Hz squared?} for the S=1, for the N = 4000, while for the S=1/2 the value of the Cramer-Rao bound reads as \vvv{XXX} which is \vvv{YYYY} time smaller. \\
The striking difference to the $S=1$ Fisher Information Matrix is the behavior of the defect with $S=1/2$.
First of all, for both spin $S=1/2$ and $S=1$, the sequence's spectral resolution is limited by the $T_1$ relaxation time of the electron spin.
On the other hand, the sequence's sensitivity is limited by $T_2$.
The main principle of 5-pulse ESEEM \cite{kasumaj20085} is to create entanglement (via, e.g., Hahn-echo or CPMG block) before the free evolution of the nuclear spins and then to apply a second correlating sequence afterwards.
In other words, the initial density matrix for the Ramsey sequence is modified so that entanglement already exists in the electron polarization terms of the density matrix, thus limited by $T_1$ time.
Fig \ref{fig:seqs} shows the sequence, which can be interpreted as two Hahn Echos separated by a long free evolution $T\gg T_2^\ast$ such that the coherence of the electron spin vanishes. The analytical formula for this sequence is provided in the appendix \ref{app:5pESEEM}.
During the free evolution time, each nuclear spin oscillates with one of two resonance frequencies obtained from Eq. \ref{eq:H}.
\begin{figure*}[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} assuming the electron spin 1/2 system. b. Enhancing the sensitivity to weakly coupled spins by increasing number of $\pi$-pulses to $N=72$ pulses in each entangling period. $\tau$ is set to the Larmor bright spot. Simulated Fisher information for the case of the electron spin c. one d. one-half system.}
		\label{fig:ddeseem}
	\end{center}
\end{figure*}

Fig. \ref{fig:ddeseem} shows the Fourier transform of the signal.
Zooming into the area close to the Larmor frequency reveals the weakly coupled nuclei.
Each nuclear spin has two peaks in the spectrum referring to $\omega_a$ and $\omega_b$. Expanding the resonance frequencies up to first order with respect to hyperfine coupling shows that nuclear spins appear in order of their coupling strength, making their characterization rather straightforward.
To observe the weakly coupled nuclei more pronouncedly, one can use the DD-ESEEM sequence by adding more $\pi$ pulses in the entangling periods.
To distinguish other nuclei, extra measurements are required.
One method is to use two-dimensional hyperfine correlation spectroscopy (2D Hyscore) \cite{vorobyov2022addressing}.
However, this method is rather time-consuming as two time variables have to be swept.
Optimum time sampling techniques might be used to optimize the timing of 2D sampling.
Here we suggest an alternative way, which is conventionally used in ESR, i.e., sweeping the $\tau$ parameter and keeping track of the frequency amplitude as a function of $\tau$.
Two frequencies that belong to the same nucleus are correlated because the modulation depth oscillates with blind spot terms of both frequencies $\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})$.
Fig. \ref{fig:5} shows two frequencies going to bright and blind spots simultaneously.
Hence, by taking a two-dimensional correlation of the spectrum, one can deduce which two frequencies are correlated and belong to the same nucleus.

@@

Next, we approach the estimation of the number of nuclear spins that could be identified. It depends on the duration of free evolution time and the choice of inter-pulse timing $\tau$.

\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/fig5.png}
		\caption{a. FFT of ESEEM signal for $\tau$ from 10 $\mu$s to 500 $\mu$s with the step of 10 $\mu$s b. 2D correlation of each frequency for different $\tau$.}
		\label{fig:5}
	\end{center}
\end{figure*}

\section{Discussion}
\label{sec:discussion}
%\subsection{Advanced filters}
Here is the concise conclusion

>>>>

%%%%%%%%%%%%%%%%%%%================= %THEORY
\section{Results}
\label{sec:theory}
\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} assuming the electron spin is a. spin 1 system b. spin 1/2 system. Simulated Fisher information matrix for the case of the electron spin c. spin 1 system d. spin 1/2 system.}
		\label{fig:3}
	\end{center}
\end{figure*}
%%%%%%%%%%%%%%%Í%%%%=================
We consider a central spin system of \textit{non-interacting} nuclear spins $I=1/2$ coupled to the central electron spin $\boldsymbol{S}$.
The central electron spin is manipulated resonantly with microwave pulses, which transfer the population between the two sublevels denoted as $m_s=s_0$ and $m_s = s_1$.
These two spin sublevels are separated due to the Zeeman effect and/or zero-field splitting, forming a two-level subsystem with an energy splitting of $\omega_a$.
The Hamiltonian of the system in the secular approximation and in the rotating frame of the applied microwave $\omega_{mw}$ can be written as:
\begin{align}
	H = \Delta S_z + \sum_k (\omega_L^{(k)}  + A_{zz}^{(k)} S_z) I_z^{(k)} + A_{zx}^{(k)} S_z I_x^{(k)}
	\label{eq:H}
\end{align}
Where $\Delta = \omega_a - \omega_{mw}$ is the detuning, $\omega_L^{(k)} =\gamma_n^{(k)} B$ is the nuclear Rabi frequency with $\gamma_n^{(k)}$ being the nuclear spin gyromagnetic ratio and $B$ the external magnetic field, and $A_{zz}$ and $A_{zx}$ are the parallel and perpendicular secular components of the hyperfine tensor, respectively.
The Hamiltonian is diagonal in the electron spin subspace, thus the Hamiltonian for the nuclear spins could be rewritten in the electron spin subdomains $s_i$ ($i=0,1$).
The nuclear spin Hamiltonian could be solved for eigenenergies, which determine the precession frequencies of $\omega_i = \sqrt{(\omega_L + s_i A_{zz})^2+ (s_i A_{zx})^2}$, $i=0,1$ along the eigenvector axes $\vec{n}i =(\frac{s_i A{zx}}{\omega_i}, 0, \frac{\omega_L + s_i A_{zz}} {\omega_i})$.
It is assumed that the pulse duration $t_p$ is short enough ($\omega_L t_p \ll 1$) that the nuclear spin dynamics during this time is negligible.
For completeness, we start our analysis with the simplest characterization sequence, which is the electron spin Ramsey sequence (free induction decay of the electron) (see the Appendix for derivation).
The Ramsey signal can be obtained as follows:
\begin{gather}
	\expval{\sigma_z}_{Ram} = \cos(\Delta \tau) \prod_{j=1}^{n} \Big[ \cos(\frac{\omega_0 \tau}{2}) \cos(\frac{\omega_1 \tau}{2})+ \notag \\
	(\vec{n_0}\cdot \vec{n_1})\sin(\frac{\omega_0 \tau}{2}) \sin(\frac{\omega_1 \tau}{2}) \Big]^{(j)}
	\textcolor{gray}{e^{-(\frac{\tau}{T_2^\ast})^m}}
\end{gather}	
The exponential decay is introduced to note the Ramsey signal decays with the electron spin $T_2^\ast$ since the formalism does not account for any relaxation processes. The Ramsey sequence is sensitive to detuning since the electron spin is not refocused; however, it is possible to sense nuclear spins with vanishing perpendicular hyperfine coupling.\\

@@

Although the Dynamical Decoupling (DD) sequence is well understood and used to characterize nuclear spins, it is not applicable to all systems.
First, DD only works for defects with high magnetic fields and low hyperfine coupling ($\omega_L \gg A_{zz}, A_{zx}$).
Second, the signal is limited to the electron spin $T_2$, which only gradually approaches $T_1$.
Third, signal analysis is rather complicated and time-consuming; one has to collect enough data to ensure that no two nuclear spins overlap in the signal.
Fourth, this sequence does not work for spin 1/2 systems, such as group IV defects in diamond, since the parallel component of the hyperfine coupling cancels their effect on the first order electron spin signal.
Hence, the resonance signal depends on the second order of the perpendicular hyperfine component.
\begin{figure*}[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} assuming the electron spin 1/2 system. b. Enhancing the sensitivity to weakly coupled spins by increasing number of $\pi$-pulses to $N=72$ pulses in each entangling period. $\tau$ is set to the Larmor bright spot. Simulated Fisher information for the case of the electron spin c. one d. one-half system.}
		\label{fig:ddeseem}
	\end{center}
\end{figure*}

In this work, we consider the 23-nuclear spin cluster characterized in paper \cite{abobeih2019atomic} as a realistic case for our comparison.
First, we apply this to the dynamical decoupling sequence and visualize the obtained results. Fig \ref{fig:3} compares the DD signal for the same nuclear spin register but different defects in diamond.
An intuitive description of the sensitivity of a sequence to the variation of hyperfine coupling could be estimated by considering the width and sensitivity of the position of the resonances.
First, we consider the case of an NV center in diamond. The width of a dip is $\delta \tau = \frac{A_{zx}}{\omega_L^2}$. Taking the derivative of the resonance time, we define the sensitivity of the longitudinal hyperfine coupling as follows, using Eq. \ref{eq:resonance} to simplify:
\begin{gather}
	\delta A_{zz} \equiv \frac{\delta \tau}{\abs{\frac{\partial \tau_p}{\partial A_{zz}}}} = \frac{2}{\tau_p} \frac{A_{zx}}{\omega_L} \ge \frac{4}{T_2^{HE}} \frac{A_{zx}}{\omega_L}
\end{gather}
If we assume typical values of $T_2^{HE} = 100$ $\mu$s and $\omega_L=500$ kHz, a weakly coupled nuclear spin $A_{zx}=5$ kHz can be distinguished from another weakly coupled nuclear spin with $\delta A_{zz} = 400$ Hz.
For $S=1/2$, such as group IV defects in diamond, the resonance times are sensitive to the second order of $A_{zx}$ and show no sensitivity to $A_{zz}$.
Hence, even at large $\tau$, the resonances related to nuclear spins will not be well separated.
We define the sensitivity for the spin one-half system as follows:
\begin{gather}
	\delta A_{zx} \equiv \frac{\delta \tau}{\abs{\frac{\partial \tau_k}{\partial A_{zx}}}} = \frac{4}{\tau_k} \ge \frac{8}{T_2^{HE}}
\end{gather}
Assuming typical values of $T_2^{HE} = 100$ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate and approximately 160 times worse than for $S=1$.
\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/fig5.png}
		\caption{a. FFT of ESEEM signal for $\tau$ from 10 $\mu$s to 500 $\mu$s with the step of 10 $\mu$s b. 2D correlation of each frequency for different $\tau$.}
		\label{fig:4}
	\end{center}
\end{figure*}

To quantify the difference in sensitivity to estimating the hyperfine parameters, we perform calculations of the Fisher Information Matrix (FIM) for the 23-nuclear spin cluster, with 23 $A_{zz}$ and 23 $A_{zx}$ parameters (see Fig. \ref{fig:3}c,d).
The Fisher Information Matrix is estimated for the probability to measure state $|0\rangle$ and reads as: 
\begin{equation}
	F_{ij}(\textbf{A})=\sum_\tau \frac{\partial p(0, \tau, \textbf{A})}{\partial A_i}\frac{\partial p(0, \tau, \textbf{A})}{ \partial A_j} \frac{1}{p (1-p)}.
\end{equation}
For the typical case of an NV center with $S=1$, since all the nuclear spin resonances are clearly resolved, the Fisher Information Matrix takes a diagonal shape, revealing low covariance between the various nuclear spin resonances.
There is crosstalk between $A_{zz}$ and $A_{zx}$ for a nuclear spin, as the position of the peaks depends on both values.
The Fisher Information provides a bound for the precision of parameter estimation, known as the Cramér–Rao bound: 
\begin{equation}
	\delta A^2 \ge \frac{1}{N} F(A)^{-1}
\end{equation}
The striking difference to the $S=1$ Fisher Information Matrix is the behavior of the defect with $S=1/2$.
First of all, for both spin $S=1/2$ and $S=1$, the sequence's spectral resolution is limited by the $T_1$ relaxation time of the electron spin.
On the other hand, the sequence's sensitivity is limited by $T_2$.
The main principle of 5-pulse ESEEM \cite{kasumaj20085} is to create entanglement (via, e.g., Hahn-echo or CPMG block) before the free evolution of the nuclear spins and then to apply a second correlating sequence afterwards.
In other words, the initial density matrix for the Ramsey sequence is modified so that entanglement already exists in the electron polarization terms of the density matrix, thus limited by $T_1$ time.
Fig \ref{fig:seqs} shows the sequence, which can be interpreted as two Hahn Echos separated by a long free evolution $T\gg T_2^\ast$ such that the coherence of the electron spin vanishes. The analytical formula for this sequence is provided in the appendix \ref{app:5pESEEM}.
During the free evolution time, each nuclear spin oscillates with one of two resonance frequencies obtained from Eq. \ref{eq:H}.

\label{sec:discussion}
\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=1.0\textwidth]{pict/cov_compare_vad.pdf}
		\caption{Visualisation of the CramerRao bound for various protocols on existing nuclear spin dataset from \cite{Abobei2019}}
		\label{fig:cov}
	\end{center}
\end{figure*}
Fig. \ref{fig:ddeseem} shows the Fourier transform of the signal.
Zooming into the area close to the Larmor frequency reveals the weakly coupled nuclei.
Each nuclear spin has two peaks in the spectrum referring to $\omega_a$ and $\omega_b$. Expanding the resonance frequencies up to first order with respect to hyperfine coupling shows that nuclear spins appear in order of their coupling strength, making their characterization rather straightforward.
To observe the weakly coupled nuclei more pronouncedly, one can use the DD-ESEEM sequence by adding more $\pi$ pulses in the entangling periods.
To distinguish other nuclei, extra measurements are required.
One method is to use two-dimensional hyperfine correlation spectroscopy (2D Hyscore) \cite{vorobyov2022addressing}.
However, this method is rather time-consuming as two time variables have to be swept.
Optimum time sampling techniques might be used to optimize the timing of 2D sampling.
Here we suggest an alternative way, which is conventionally used in ESR, i.e., sweeping the $\tau$ parameter and keeping track of the frequency amplitude as a function of $\tau$.
Two frequencies that belong to the same nucleus are correlated because the modulation depth oscillates with blind spot terms of both frequencies $\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})$.
Fig. \ref{fig:4} shows two frequencies going to bright and blind spots simultaneously.
Hence, by taking a two-dimensional correlation of the spectrum, one can deduce which two frequencies are correlated and belong to the same nucleus.

@@

Next, we approach the estimation of the number of nuclear spins that could be identified. It depends on the duration of free evolution time and the choice of inter-pulse timing $\tau$. For the realistic case of the $T_1 = 1$ s, and $T_2 = 100 \mu s$, we approach the estimation of the Fisher information matrix for various protocols and approach the system with moderate N=16 pulses for the dynamical decoupling sequence and simplest 5 pulse ESEEM for correlation protocol for simplicity of calculation, since in that case the analytical expressions are available.

On Fig. \ref{fig:cov} we see a manifestation of the correlation protocol for spin 1/2 system realised in a number of nuclear spins one could estimate with each of the protocols. 
The figure presents the dots, in the $A_{zz}, A_{zx}$ axes, with an area bounded by Cramer-Rao bound around each point. 
When uncertainty is larger the absolute values of the coupling, the point is considered to be non-detectable or if it is larger than the distance to the nearest point non distinguishable and is marked in red.
Alternatively, it is considered to be identified and is turned blue. 
Additionally, we plot an ellipses, with two points as it foci and small axis size as a value of the covariance between various parameters in the Cramer-Rao bound. 
We plot only single ellipse with largest covariance value. 
This values are calculated as off-diagonal elements in the inverse Fisher information matrix. 
This covariances are mostly show the crosstalk between different parameters in the presented data, and are more strongly present in the DD S=1/2 case. 
The idea behind ellipse representation, is that when the covariance is larger than the self-variance, the ellipse absorbs the individual points, and the points become indistinguishable. 
We find that, while this crosstalk is not the limiting factor for informational approach, it might be important when a realistic estimator is considered. 
We note, that this is not strictly same condition as in the experimental identification, and is idealised. 
We only consider the available information in the plot, assuming that an optimum estimator for extraction of that information already exist. 
In reality, one has to additionally assume a non ideal estimator procedure, which involves extraction of the hyperfine parameter values from the raw data and is a subject of further work.
As a result we see, that while for the DD method, a S=1/2 case for N=16 pulses allows for identification of only 3 spins out of 23, the 5 pulse ESEEM method works with similar success for both S=1 and S=1/2 system. 
Totally, it is capable of detecting 15-17 nuclear spins, and could be further boosted by usage of DD-ESEEM method with multiple pulses in each sensing block analogous to Fig. \ref{fig:ddeseem}

\section{Discussion}

%\subsection{Advanced filters}
In this work we performed a theoretical and numerical comparison of various ESEEM methods for the purpose of characterisation of the nuclear spin clusters around S=1 and S=1/2 type of defects.
We found, that while for S=1 systems, modified spin echo sequences, e.g. CPMG and XY-N, are most suited for single nuclear spin qubit spectroscopy, for S=1/2 system they are limited in performance. 
We see, that a correlation type sequences, e.g. 3,5 pulse ESEEM present a more potential for characterisation of a diluted nuclear spin bath, and perform at least similar to the S=1 case. 
We believe, that this method boast large potential for preliminary screening of nuclear spin clusters for S=1/2 potential qubit candidate systems, such as G-IV defects in diamond. Additionally, our method does not require strong microwave pulse fields, since the pulses do not require to cope with nuclear spin Larmour frequency.
